### 2021-06-18 background.tex
Background.tex

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

>>>>

\kn{This section starts abrupt. We should have a line that says what concepts we introduce on a high level. Also, I feel "sandbox" itself should be one of the backgrounds and have a textbf after the introductory line.}
A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.
